\documentclass[report]{IEEEtran}
\usepackage{blindtext}

%\title{Bitcoin Security}
%\author{Garret Tonra - G00341908 }
%\date{\today}

\begin{document}
\title{How Secure is Bitcoin ? }
\author{by Garret Tonra % <-this % stops a space
\thanks{.\newline Garret Tonra Current Fourth Year
Software Development Student Studying in the Galway-Mayo Institute of Technology, Old Dublin Rd, Galway, Ireland 
e-mail: g00341908@gmit.ie}% <-this % stops a space
}

\maketitle

\begin{abstract}
Text for abstract
\end{abstract}


\section{Introduction}.\newline
The Emerging Technology that I am focusing on for my Literature Review is Bitcoin. So what exactly is Bitcoin?\newline
Bitcoin is basically the first ever created decentralized digital Currency. Bitcoin was first created in 2009 by a unknown entity or entities taking the name of Satoshi Nakamoto. that person or persons are still anonymous to this present day. When creating bitcoin Satoshi had also implemented the first ever blockchain database. Bitcoin is known as a peer-2-peer system or P2P\newline It is a transaction system that takes out the middleman in most cases the banks. This results in a very low transaction costs for a user. Bitcoin can be used to pay for virtually anything you want, It is a neutral currency. Bitcoin Transactions are managed by miners these are people who verify P2P transactions and are rewarded by newly generated Bitcoins. Once the transactions are verified by the miners they are then recorded and saved in the Public Ledger. Since bitcoins emergence in 2009 it has steadily grown and is used more and more frequently as a means of paying for goods and services but is bitcoin a secure form of Currency or is it too early to know in the next sections I shall be looking at this cryptocurrency and how its design is secure?

\section{Blockchain}.\newline
Blockchain technology is the essential component to bitcoins goal of the P2P system,Since the blockchain is a decentralized system meaning it does not need a trusted 3rd party to make transactions \newline Blockchain stores the transaction information of every single transaction ever made across a network of personal computers,Which means that no central company or person owns the blockchain system but everybody can still access it and help to maintain and run it. The Blockchain is the fundamental piece of the puzzle that makes a P2P system very hard to compromise,as it has no central point to attack,compared to a Trusted party system where there usually main point of centralization.where a blockchains security is stronger compared to a centralized point system is the way it is structured together each block that is  a verified transaction is added to the chain. Inside that block it has the cryptographic hash value of the previous block. This previous hash value then acts as a unique ID for the previous block. From this system the blockchain implements a log system of all transactions that have ever taken place. Starting back from the first block created the "Genesis Block". Thus this system can verify every transaction ever completed and calculate the value of every piece of a bitcoin address. As well as that every node that was or will be offline will be easily able to reach the most up to date  block by reading a few recent blocks that were missing. The blockchain is always increasing. Adding from the previous block and in turn referencing that blocks unique cryptographic hash value each time a new one is added. The are always vasts amounts of new blocks inside the network so to ensure a consistent chain blocks are only allowed to have transactions that are matching the current balance of the previous chain. If the Nodes hold the same copy of the blockchain then we can actually account for every piece of the bitcoin as well as the ownership of each piece as long as all the nodes have the same copy of the blockchain. Since this is not a centralized system it is not fool proof. If two blocks are created at roughly the same time and they are created by different nodes. Then the different nodes might branch from the same parent but have two different chains which will show different versions of the transactions log. If this happens then how does the blockchain figure out which is the right log ?. Here is where the  Protocol is Essential to the system it blockchain has two mechanisms to essentially prevent this sort of chain forking simply by making blocks quite hard to create the way it makes blocks hard to create is by insisting on each block to have a "Proof of Work"   
\end{document}